1. Original Data

### 2021-06-30 analysis/reports/rmd/01_dataGMTV.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty) to visit the corresponding Github repository.

This report is the first in a series of reports covering this project. It prepares the original data and replicates main visualizations & tables.

@@

Within the appendix, one also learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9. Subsetting the data correspondingly yields a `data.table` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

In an attempt to incorporate uncertainty to @GACHTER2017's dynamic public goods game (DPGG), I plan to run a series of remote online experiments using oTree [@oTree]. The first experiment will replicate Gächter et al.'s NOPUNISH 10-period version as close as possible (given the remote circumstances). The current demo version of the experiment can be found [here](https://cliccs.herokuapp.com/). Click [here](https://github.com/Howquez/coopUncertainty/tree/July21Replication) to visit the corresponding Github repository.

[This report](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd/01_dataGMTV.Rmd) is the first in a series of reports covering this project. It prepares the original data and replicates main visualizations & tables.

@@

Within the appendix, one  learns that the NOPUNISH 10-period data were collected in sessions 5, 8 and 9. Subsetting the data correspondingly yields a `data.table` consisting of 23 observations and $4 \times 10 \times 23=$ `r NROW(noPunish10)` rows and 27 variables.
